---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# bjpack1
The goal of bjpack1 is to create a table that includes all of the important performance measures of classifier to intuitively provide important information at once that is necessary for the comparison of the models' performance, to create a ROC with useful information of the best model in a neat way, to create a PRC for each model, and to create a shiny gadget that provides a ROC/PRC according to a user's choice.

## Installation

You can install the development version of bjpack1 like so:

``` r
install.packages("bjpack1")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r data example}
library(bjpack1)

## basic example code
testy<-sample(c(0,1), 154, replace=TRUE)
pred_test1<-runif (154, min=0, max=1)
pred_test2<- runif (154, min=0, max=1)
predlist<-list(pred_test1, pred_test2)
modellist<-list("Randomforest","Decision tree")
```

```{r newtab, echo=FALSE}
##measure table
newtab=modelmeasure(testy, predlist,modellist)
plot(newtab)
```

```{r newroc, echo=FALSE}
##roc
newroc=bjroc(testy, predlist,modellist)
plot(newroc)
```
```{r prc, echo=FALSE}
#prc
apr=bjpr(testy, pred_test1, "Randomforest")
bpr=bjpr(testy, pred_test2, "Decision tree")
#install.packages("ggpubr", repos = "http://cran.us.r-project.org")
library(ggpubr)
prc=ggarrange(apr, bpr, labels=c('A','B'))
plot(prc)
```
```{r bjshiny function example}
##shiny gadget
newshiny=bjshiny (testy, pred_test1,modellist)
```


